Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added TODOs for existing NN
Added lots of TODOs

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $DeepConv(\omega)$ & 77\% & TODO \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & TODO \\
    \hline
\end{tabular}

@@

This system was trained using $FourierMLP(\beta_{8})$ for $NN(x)$, because this was the most successful configuration in supervised learning. It produced the highest accuracy as well as the lowest class-wise standard deviation.

@@

The following table directly compares performance of the semi-supervised learning systems, with the existing PICO-60 neural network provided as a baseline once again. Note that ``Max Accuracy'' refers to accuracy at replication of Acoustic Parameter, rather than replication of the ground truths.

\begin{tabular}{|l|l|l|l|}
    \hline
    Technique & Max AP Accuracy & Max Mean by Run & $\varsigma$ Errors: 128 versus 256 \\
    \hline
    Gravitational Differentiation & 98\% & 96\% & 64\% Increase \\
    \hline
    Iterative Cluster Nucleation & 100\% & 98\% & 85\% Increase \\
    \hline
\end{tabular}

>>>>

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $DeepConv(\omega)$ & 77\% & TODO \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & TODO \\
    \hline
    Existing NN TODO & X & X \\
    \hline
    AP TODO & X & X \\
    \hline
\end{tabular}

@@

This system was trained using a multi-layer perceptron with an 8-band Fourier transform input for $NN(x)$, because this was one of the most successful configurations in supervised learning. It produced the highest accuracy as well as the lowest class-wise standard deviation.

@@

The following table directly compares performance of the semi-supervised learning systems, with the existing PICO-60 neural network provided as a baseline once again. Note that ``Max AP Accuracy'' refers to accuracy at replication of Acoustic Parameter, rather than replication of the ground truths.

\begin{tabular}{|l|l|l|}
    \hline
    Technique & Max AP Accuracy & Max Mean by Run \\
    \hline
    Gravitational Differentiation (256 $\varsigma$) & 98\% & 96\% \\
    \hline
    Gravitational Differentiation (128 $\varsigma$) & TODO & TODO \\
    \hline
    Iterative Cluster Nucleation (256 $\varsigma$) & 100\% & 98\% \\
    \hline
    Iterative Cluster Nucleation (128 $\varsigma$) & TODO & TODO \\
    \hline
    Existing NN TODO & X & X \\
    \hline
    AP TODO & X & X \\
    \hline
\end{tabular}
